Combined Task and Motion Planner through an Interface Layer

### 2015-04-17 documentation/draft.tex

-realistic expectations for someone interested in applying the reasoning technique

-still need to get a motion planner and a task planner working and need to make them have the right API interface -- not a pure out of the box working thing

-is not guaranteed to find an optimal solution

-cannot do online re-planning

-time to run is based on speed of the motion planner and task planner

>>>>

The most important limitation of this implementation is to remember that it is an interface layer.  
It does not include a task planner and a motion planner: you must set those up yourself as ROS services and make sure that the output and input message types specify those outlined in the API.  
Depending on what planners you use, setting them up and installing them may be nontrivial.  
Different planners are effective for different tasks and some planners may require extensive installation.  
When you pick your task and motion planners, remember that this interface layer is set up to only work with task planners that use the PDDL specification language.  
If you choose to use another specification system, you will need to translate between PDDL and your system.

On a more detailed level, it is important to note that this planner is not guaranteed to find an optimal solution, or even to find a solution at all.  
We refer you to [1] for a proof that this algorithm is guaranteed to find a solution for problems with certain properties.  
However, due to the random nature of the pose generators and that there are limits set on the number of iterations, a valid plan may not be found for all problems.

Furthermore, this system is not intended for online replanning.  
It may be possible to use it for online replanning for some systems if it runs quickly on the particular problem, but it is not an intended feature of this algorithm.

Finally, the runtime of this algorithm is based on the speed of the motion planner and the task planner used within it.  
If the motion planner and task planner are not efficient, the interface layer will not produce answers quickly.
